The Privacy of Private Browsing

### 2013-12-14 finalproject/paper.tex
added definitions section

    \subsection{What Private Browsing Is Not}
    The private browsing modes of Firefox, Chrome, and Internet Explorer are
    designed with the intent of preventing users of the same computer from
    determining what someone was doing on that computer. They do not attempt
    to keep a user's internet activities hidden from that user's internet
    service provider (ISP), and they do not prevent websites from identifying
    that user.\cite{verdi13}\cite{google13}\cite{ie13}

@@

    \subsection{Where To Look}
    Focused analysis of the hard drive itself can reveal the most artifacts.
    One private browsing experiment in which logon information, browser
    history, and cached images were recovered obtained most of the artifacts
    from portions of the hard disk known as \emph{free space} and \emph{slack
    space}.\cite{ohana13} Free space refers to a group of hard drive sectors 
    (called a \emph{cluster}) that is not allocated to any particular file.
    Slack space,on the other hand, refers to the space between the end of a 
    file and the end of the cluster in which it is stored. Hard drive clusters 
    are of a fixed size determined by the operating system. Most of the time, 
    when a user saves a file to his or her hard drive, the file is not exactly 
    the same size as the cluster in which the operating system puts it.
    Furthermore, when a user ``deletes'' a file from his or her hard drive, the
    file is not really deleted---it is simply marked as available to be
    overwritten if necessary. If a file is eventually stored on the hard drive
    in a cluster that used to be home to a larger (now ``deleted'') file,
    leftover data from the old file will still exist at the end of that
    cluster.

@@

    \subsection{Firefox}

>>>>

	\subsection{Definitions}
	Many shortcomings of private browsing modes relate to how a computer's 
	operating system manages memory and disk space. Those who are unfamiliar
	with these tasks may benefit from the definitions below.

	\begin{description}
	  \item[Cluster] A group of disk sectors that the operating system
	  treats as a unit; smallest unit of disk storage that the operating
	  system can allocate
	  \item[Disk] The hard drive of a computer; where a user's files and
	  directories (among other things) are stored
	  \item[Free space] A cluster that is not allocated to any particular 
	  file
	  \item[Page] The smallest unit of memory that the operating system can
	  allocate; can be temporarily stored on disk to allow the computer to run
	  more programs at the same time
	  \item[Slack space] The space between the end of a file and the end of 
	  the cluster in which it is stored; important in computer forensics for
	  finding fragments of old files\footnote{Hard drive clusters are of a 
	  fixed size determined by the operating system. Most of the time, when a 
	  user saves a file to his or her hard drive, the file is not exactly the 
	  same size as the cluster in which the operating system puts it. 
	  Furthermore, when a user ``deletes'' a file from his or her hard drive, 
	  the file is not really deleted---it is simply marked as available to be
      overwritten if necessary. If a file is eventually stored on the hard 
	  drive in a cluster that used to be home to a larger (now ``deleted'') 
	  file, leftover data from the old file will still exist at the end of that
      cluster.}
	\end{description}

@@

    \subsection{Where To Look}
    Focused analysis of the hard drive itself can reveal the most artifacts.
    One private browsing experiment in which logon information, browser
    history, and cached images were recovered obtained most of the artifacts
    from the hard drive's free space and slack space.\cite{ohana13}

@@

    \subsection{Firefox}
	In 2011, researchers discovered that Firefox 3.6.11 stored browser history
	and search engine keywords in the computer's physical memory and that this
	information could be accessed after the browsing session was terminated.
	An analysis of the contents of pagefile.sys revealed similar information.
	\cite{said11} Additionally, certificate chains received during private 
	browsing sessions in Firefox 3.6 were not removed from their on-disk 
	database once the browsing session was terminated.
